---
title: "Efficient R by Colin Gillespie and Robin Lovelace, My Notes"
output: html_notebook
---

## Book resources

```{r}

# debug(devtools::install_github("csgillespie/efficient"))
# devtools::install_github("csgillespie/efficientR")
# devtools::install_github("csgillespie/efficient", build_vignettes = TRUE)

library("microbenchmark")
library("profvis")
library("ggplot2")

```


## Efficient setup

Two files are read each time R starts (unless one of the command line options outlined above is used):

* .Renviron sets environment variables. These tell R where to find external programs and can hold user-specific information than needs to be kept secret, typically API keys.

* .Rprofile is a plain text file (which is always called .Rprofile, hence its name) that simply runs lines of R code every time R starts. If you want R to check for package updates each time it starts (as explained in the previous section), you simply add the relevant line somewhere in this file.

Files in three folders are important in this process:

* R_HOME, the directory in which R is installed. The etc sub-directory can contain start-up files read early on in the start-up process. Find out where your R_HOME is with the R.home() command.

* HOME, the user's home directory. Typically this is /home/username on Unix machines or C:\Users\username on Windows (since Windows 7). Ask R where your home directory is with, Sys.getenv("HOME").

* R's current working directory. This is reported by getwd().

```{r echo=TRUE}

R.home()
Sys.getenv("HOME")
getwd()

```

### To check for site-wide .Rprofile
```{r}
site_path = R.home(component = "home")
fname = file.path(site_path, "etc", "Rprofile.site")
file.exists(fname)
```



## Loading R packages

This is a good [link with "proper solution" of changing Windows environment variable]( https://stackoverflow.com/questions/15170399/changing-r-default-library-path-using-libpaths-in-rprofile-site-fails-to-work) but I think easier is here at https://stackoverflow.com/questions/31707941/how-do-i-change-the-default-library-path-for-r-packages


```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
